Chasing \rainbows{} with the Habitable Worlds Observatory

### 2023-03-10 src/tex/ms.tex
[showyourwork] overleaf sync

In practice, the clouds complicate the detection of ocean glint because they obscure the underlying surface and they are themselves non-Lambertian scatterers. \cite{Zugger_2010} simulated photometric and polarized phase variations for planets including the effects of partial cloud coverage and ocean waves. Although the presence of clouds and atmospheric Rayleigh scattering weaken the signal of an underlying ocean, they again find that oceans are detectable and distinguishable from other sources of polarization. \cite{2010ApJ...721L..67R} compared observations of the Earth's scattering phase curve to comprehensive radiative transfer simulations; they found that the photometric brightening of Earth at crescent phases is mostly due to forward scattering from clouds, with a relatively small contribution from ocean glint.
\citet{Zugger_2011} note that ocean glint might be observed in near infrared opacity windows, because of the reduced Rayleigh scattering at long wavelengths. This has the added advantage of minimizing the latitude--albedo effect, which could otherwise be a false-positive for photometric brightening at crescent phases due to glint \citep{2012ApJ...752L...3C}. \cite{2019A&A...626A.129T} simulated the photometric and polarimetric signatures of terrestrial planets with inhomogeneous clouds. \cite{2022A&A...664A.172T}...

>>>>

In practice, clouds complicate the detection of ocean glint because they obscure the underlying surface and are themselves non-Lambertian scatterers. \cite{Zugger_2010} simulated photometric and polarized phase variations for planets including the effects of partial cloud coverage and ocean waves. Although the presence of clouds and atmospheric Rayleigh scattering weaken the signal of an underlying ocean, they again find that oceans are detectable and distinguishable from other sources of polarization. \cite{2010ApJ...721L..67R} compared observations of the Earth's scattering phase curve to comprehensive radiative transfer simulations; they found that the photometric brightening of Earth at crescent phases is mostly due to forward scattering from clouds, with a relatively small contribution from ocean glint.
\citet{Zugger_2011} note that ocean glint is best observed in near infrared opacity windows because of the reduced Rayleigh scattering at long wavelengths. This has the added advantage of minimizing the latitude--albedo effect, which could otherwise be a false-positive for photometric brightening at crescent phases due to glint \citep{2012ApJ...752L...3C}. Most recently, \cite{2019A&A...626A.129T,2022A&A...664A.172T} simulated the photometric and polarimetric signatures of terrestrial planets with inhomogeneous clouds. The bottom line is that phase-dependent reflected light photometry and polarization of a directly-imaged exoplanet could establish its habitability.
